Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-05-19 doc/peakcharacterization_manuscript.Rmd
regenerate qcqa stuff

::: {custom-style="MDPI_2.2_heading2"}
### 2.1 Simplistically Averaged Data Have Bad Relative Intensities
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.2 m/z to Frequency
:::

@@

::: {custom-style="MDPI_3.1_text"}
FT-MS data from the Thermo-Fisher Orbitrap instruments used to acquire the data does not provide any information about the raw spectral frequency data.
Outside of the meta-data, it merely contains the m/z and intensity values for profile spectra acquired across multiple scans.
However, the spectral frequency can be calculated by dividing the midpoint m/z of two adjacent points by their difference (`r figure_count$label_text("mz_frequency_conversion")`A, red points representing the midpoint m/z of two adjacent points, length of red lines representing the difference between the two adjacent points).
The subsequent adjacent point differences in frequency are expected to be relatively constant with respect to m/z, as shown in `r figure_count$label_text("mz_frequency_conversion")`C, D and E, in contrast to the adjacent point differences in m/z, which are not constant with respect to m/z.
The Thermo-Fisher Fusion instrument from which most of our collaborators data has been acquired, at a resolution of 450K or 500K depending on the sample, has an adjacent frequency point difference mode of 0.5, as shown in  `r figure_count$label_text("mz_frequency_conversion")`D.
It is important to note that although the frequency difference has been consistent regardless of instrument resolution, we do not know a priori what it should be, and the method makes no assumptions about the frequency difference, but rather calculates the mode of the frequency differences from those observed in the data itself.
Restricting to those points that fall into a narrow range around the mode of frequency differences (0.49 - 0.51 in this work), a regression model of frequency to m/z can be generated (see Methods), with an example shown in `r figure_count$label_text("mz_frequency_conversion")`F.
This regression model seems to fit the known relationship between frequency and m/z, where the frequency is related to $1/\sqrt{mz}$.
The actual regression model used in this work includes terms of the m/z, $\sqrt{m/z}$, and $\sqrt[3]{m/z}$ (see **Conversion of m/z to Frequency** in Methods for further description of the regression model).
We did investigate a variety of frequency regression models to see which one seemed to be the best, as shown in Supplemental `r supp_figure_count$label_text("frequency_models")` and `r supp_table_count$label_text("frequency_models")`.

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.3 Sliding Window Density to Remove Noise
:::

@@

::: {custom-style="MDPI_5.1_figure_caption"}
**`r figure_count$label_text("slidingwindow_count")`.**
**A - E**: A single tiled region 2000 data points wide.
**A**: Non-zero point intensities in frequency space across all scans.
**B**: Number of non-zero points in sliding regions. Blue line indicates 99th percentile of non-zero counts in this one region.
Red line is the rounded value of median x 1.5 of 99th percentiles from **F**.
**C**: Zoomed y-axis of **B** to show the non-zero counts that are below the median cutoff.
**D**: Sliding region non-zero counts that are greater than the cutoff.
**E**: Non-zero point intensities across scans in the regions from D.
**F**: Histogram of the 99th percentile cutoffs from all of the tiled windows. Red line is the median x 1.5.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.4 Peak Characterization Using Quadratic Fit
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.5 Breaking Up Initial Regions
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.6 Normalization of Scans
:::

@@

::: {custom-style="MDPI_3.1_text"}
Due to differences in how many ions are captured in the trap and the limited dynamic range of the detector, the observed peak intensities for the same analyte vary between scans (see `r figure_count$label_text("breaking_regions")`A and B for example).
Using the median peak differences between scans, it is possible to normalize the peak intensities across scans.
However, there are two issues with these peak intensities across scans: (a) some peak intensities correlate with the scan number (i.e., scan acquisition order); and (b) some peak differences between scans are correlated with intensity.
The solution to (a) is to do a two-pass normalization.
After the first pass, the peaks whose intensity is correlated with scan order are detected (absolute Pearson correlation > 0.5).
In the second pass, the correlated peaks are removed, and normalization is carried out again.
`r figure_count$label_text("intensity_scan")`A shows an example peak whose intensity across scans is correlated with scan number.
The solution to (b) (peak differences correlated with intensity) is to only use the most intense peaks, as shown in `r figure_count$label_text("intensity_scan")`B.
The highlighted peaks in `r figure_count$label_text("intensity_scan")`B are those with an intensity greater than 0.7 of the maximum intensity observed in that scan, and at least visually, their differences are **not** correlated with intensity.
If *all* peaks are used for normalization, a very different set of normalization factors will be generated than by using only the *most intense* peaks, as shown in `r figure_count$label_text("normalization_factors")`A and B.
Though the two-pass normalization (doublenorm) and single-pass normalization using the most intense peaks (singlenorm_int) generate very similar normalization factors (`r figure_count$label_text("normalization_factors")`B and C), which is expected as they both use the most intense peaks. 
But removing the scan-correlated peaks does change the majority of the normalization factors.
:::

@@

::: {custom-style="MDPI_5.1_figure_caption"}
**`r figure_count$label_text("normalization_factors")`.** **A**: Histogram of scan normalization factors using either a single-pass normalization using *all* peaks (singlenorm), single-pass normalization using peaks with an intensity ≥ 0.7 of the maximum intensity (singlenorm_int), or the two-pass normalization removing peaks whose height is correlated with scan and using the most intense peaks (doublenorm).
**B**: The difference of the normalization factors obtained from either doublenorm or singlenorm_int compared to singlenorm.
**C**: **B**, but with a zoomed y-axis to illustrate the differences in the normalization factors obtained with the different methods.
:::

::: {custom-style="MDPI_2.2_heading2"}
### 2.7 Mitigation of High Peak Density Artifacts
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.8 Changes in Relative Standard Deviation (RSD)
:::

@@

::: {custom-style="MDPI_3.1_text"}
Each step in the peak characterization either changes the overall number of peaks coming from each scan (sliding windows and breaking initial regions) or the overall intensity of the points within a scan.
Therefore, one way to quantify any potential *improvements* in the characterized peaks is to look at the relative standard deviation (RSD) for the characterized scan level peak intensities (calculated as the standard deviation of peak heights across scans divided by the mean peak height) and compare them as each processing step is introduced.
`r figure_count$label_text("rsd_method")` illustrates the peak height RSD distributions for four different samples.
Up to two modes are reported for each distribution, where a mode location is only reported if it is ≥ 0.2X the most intense mode.
For samples 1ecf and 2ecf, there is a general shift in the RSD to the left, going from the bottom processing methods (msnbase_only) to the top processing method (filtersd), representing a visually clear improvement.
For samples 49lipid and 97lipid, the improvements are visually more subtle, having a slight shift to the left as well as a narrowing and smoothing of the RSD distribution.
Part of this subtlety is likely due to the bi-modality of these two distributions.
This is not surprising, since these two samples are non-polar extractions from tissue and are biochemically more complex.
`r table_count$label_text("rsd_method")` provides more quantitative metrics.
At two decimal places, the filtersd, doublenorm, and singlenorm processing methods give superior and nearly identical results for three of the four samples, especially in terms of mean and median RSD.
However, for sample 1ecf, the max RSD is much higher for singlenorm, highlighting its instability.
:::

@@

::: {custom-style="MDPI_4.1_table_caption"}
`r table_count$label_text("rsd_method")`.
RSD means, medians, modes, and maximum observed values for each sample with different overall processing.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.9 Difference to Relative Natural Abundance
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.10 Method Specific Peaks
:::

@@

`r figure_count$label_text("assigned_mz_diff")` shows the distribution of differences between the observed and expected m/z of assigned peaks in the 1ecf and 97lipid spectra.
For the 1ecf-specific histograms, it is clear that these differences have a narrower unimodal distribution from the scan-centric peak characterization, especially in comparison to MSnbase.
Also, the MSnbase distribution has far fewer peaks that match a scan-level assigned peak.
Given the large number of MSnbase-characterized peaks present in the spectrum, many peaks may be outside the matching tolerance of 2ppm. 
This strongly implies that the peak center error is far higher in the MSnbase-characterized peaks than what the histogram directly shows.
For the 97lipid-specific histograms, again the difference distribution for the scan-centric peak characterization is narrower, but the improvement is not as pronounced, likely due to the distribution being bi-modal.
Also, far fewer Xcalibur and MSnbase characterized peaks matched assigned scan-centric peaks.
Again, this strongly implies that their peak centers have far higher error.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.11 Changes in P-Values On a Large Dataset
:::

@@

compare_sina = lung_compare %>%
  ggplot(aes(x = compare_id, y = p_diff)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_sina(alpha = 0.5) +
  geom_point(data = long_measure, aes(x = compare_id, y = value), color = "green") +
  geom_text(data = long_pvalue, aes(x = compare_id, y = -5, label = format(value, digits = 2))) +
  labs(x = "", y = "Log-P-Value Difference")

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.12 Quality Control and Quality Analysis
:::

@@

The conversion of m/z to frequency also provides opportunities to evaluate each scan and whether it should be kept for further processing.
Checks that have helped us in the development of the scan-centric peak characterization have included: (i) verifying that the ordering of data points remains identical in m/z and frequency space after conversion to frequency; and (ii) examining the R^2^ fit of the predicted frequency points to the original frequency points across scans for outliers.
A third quality control step is to examine the coefficients of the square-root term for each scan (see term **y** in Equation `r equation_count$label_text("mzfrequency")`) and look for any outliers, and remove them before continuing the sample processing.
Across the `r length(coefficients_qcqa$n_coef_out)` NSCLC raw files that completed scan-centric processing, `r sum(coefficients_qcqa$n_coef_out > 0)` had at least one scan removed based on the square-root coefficient.
`r figure_count$label_text("coefficients_qcqa")`A shows a histogram of the number of scans removed based on being outliers of the overall distribution.
`r figure_count$label_text("coefficients_qcqa")`B shows what outlier scan coefficients look like in a single sample.
:::

@@

::: {custom-style="MDPI_3.1_text"}
Finally, in the scan-scan normalization step, we require that there are at least 25 peaks in each of the scans that can be used to calculate normalization factors between the scans and the reference scan.
If there are no scans with at least 25 peaks, then the processing of that sample will error and stop.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.1 Samples and Overall Processing
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.2 Matching Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.3 Conversion of m/z to Frequency
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.4 Frequency Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.5 Interval Range Based Data
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.6 Peak Containing Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.7 Peak Detection and Centroided Values
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.8 Scan to Scan Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.9 Full Scan-Centric Characterization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.10 Correction of Height and Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.11 Marking High Frequency Standard Deviation Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.12 Calculation of Relative Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.13 Scan-Centric Peak Assignment
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.14 Consistently Assigned Lipid Spectral Feature (Corresponded Peak) Generation and Peak Intensity Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.15 Peak - Peak NAP Height Ratios
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.16 Differential Analysis of Large Dataset
:::

@@

Of the starting 181 samples, five did not finish during scan-centric characterization due to not having any scans left during normalization.
In addition, some of the samples were acquired multiple times, creating duplicate samples.
Not knowing which sample run was most appropriate to use, we removed all of the duplicated samples.
Using information-content-informed Kendall-tau correlation (ICI-Kt) [@flightInformationContentInformedKendalltauCorrelation2022], we compared the median correlations of each sample to all others in the same disease class for outliers, and removed `r n_out_vector["cancer"]` cancer and `r n_out_vector["non-cancer"]` samples.
The median ICI-Kt correlations are shown in `r supp_figure_count$label_text("icikt_outlier")`.

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.17 Software Used
:::

>>>>

::: {custom-style="MDPI_2.2_heading2"}
### 2.1. Simplistically Averaged Data Have Bad Relative Intensities
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.2. m/z to Frequency
:::

@@

::: {custom-style="MDPI_3.1_text"}
FT-MS data from the Thermo-Fisher Orbitrap instruments used to acquire the data does not provide any information about the raw spectral frequency data.
Outside of the meta-data, it merely contains the m/z and intensity values for profile spectra acquired across multiple scans.
However, the spectral frequency can be calculated by dividing the midpoint m/z of two adjacent points by their difference (`r figure_count$label_text("mz_frequency_conversion")`A, red points representing the midpoint m/z of two adjacent points, length of red lines representing the difference between the two adjacent points).
The subsequent adjacent point differences in frequency are expected to be relatively constant with respect to m/z, as shown in `r figure_count$label_text("mz_frequency_conversion")`C, D and E, in contrast to the adjacent point differences in m/z, which are not constant with respect to m/z.
The Thermo-Fisher Fusion instrument from which most of our collaborators data has been acquired, at a resolution of 450K or 500K depending on the sample, has an adjacent frequency point difference mode of 0.5, as shown in  `r figure_count$label_text("mz_frequency_conversion")`D.
It is important to note that although the frequency difference has been consistent regardless of instrument resolution, we do not know a priori what it should be, and the method makes no assumptions about the frequency difference, but rather calculates the mode of the frequency differences from those observed in the data itself.
Restricting to those points that fall into a narrow range around the mode of frequency differences (0.49 - 0.51 in this work), a regression model of frequency to m/z can be generated (see Methods), with an example shown in `r figure_count$label_text("mz_frequency_conversion")`F.
This regression model seems to fit the known relationship between frequency and m/z, where the frequency is related to $1/\sqrt{m/z}$.
The actual regression model used in this work includes terms of the m/z, $\sqrt{m/z}$, and $\sqrt[3]{m/z}$ (see **Conversion of m/z to Frequency** in Methods for further description of the regression model).
We did investigate a variety of frequency regression models to see which one seemed to be the best, as shown in Supplemental `r supp_figure_count$label_text("frequency_models")` and `r supp_table_count$label_text("frequency_models")`.

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.3. Sliding Window Density to Remove Noise
:::

@@

::: {custom-style="MDPI_5.1_figure_caption"}
**`r figure_count$label_text("slidingwindow_count")`.**
**A - E**: A single tiled region 1000 frequency wide.
**A**: Non-zero point intensities in frequency space across all scans.
**B**: Number of non-zero points in sliding regions. Blue line indicates 99th percentile of non-zero counts in this one region.
Red line is the rounded value of median x 1.5 of 99th percentiles from **F**.
**C**: Zoomed y-axis of **B** to show the non-zero counts that are below the median cutoff.
**D**: Sliding region non-zero counts that are greater than the cutoff.
**E**: Non-zero point intensities across scans in the regions from D.
**F**: Histogram of the 99th percentile cutoffs from all of the tiled windows. Red line is the median x 1.5.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.4. Peak Characterization Using Quadratic Fit
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.5. Breaking Up Initial Regions
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.6. Normalization of Scans
:::

@@

::: {custom-style="MDPI_3.1_text"}
Due to differences in how many ions are captured in the trap and the limited dynamic range of the detector, the observed peak intensities for the same analyte vary between scans (see `r figure_count$label_text("breaking_regions")`A and B for example).
Using the median peak differences between scans, it is possible to normalize the peak intensities across scans.
However, there are two issues with these peak intensities across scans: (a) some peak intensities correlate with the scan number (i.e., scan acquisition order); and (b) some peak differences between scans are correlated with intensity.
The solution to **a** is to do a two-pass normalization.
After the first pass, the peaks whose intensity is correlated with scan order are detected (absolute Pearson correlation > 0.5).
In the second pass, the correlated peaks are removed, and normalization is carried out again.
`r figure_count$label_text("intensity_scan")`A shows an example peak whose intensity across scans is correlated with scan number.
The solution to **b** (peak differences correlated with intensity) is to only use the most intense peaks, as shown in `r figure_count$label_text("intensity_scan")`B.
The highlighted peaks in `r figure_count$label_text("intensity_scan")`B are those with an intensity greater than 0.7 of the maximum intensity observed in that scan, and at least visually, their differences are **not** correlated with intensity.
If *all* peaks are used for normalization, a very different set of normalization factors will be generated than by using only the *most intense* peaks, as shown in `r figure_count$label_text("normalization_factors")`A and B.
Though the two-pass normalization (doublenorm) and single-pass normalization using the most intense peaks (singlenorm_int) generate very similar normalization factors (`r figure_count$label_text("normalization_factors")`B), which is expected as they both use the most intense peaks. 
But removing the scan-correlated peaks does change the majority of the normalization factors.
:::

@@

::: {custom-style="MDPI_5.1_figure_caption"}
**`r figure_count$label_text("normalization_factors")`.** **A**: Histogram of scan normalization factors using either a single-pass normalization using *all* peaks (singlenorm), single-pass normalization using peaks with an intensity ≥ 0.7 of the maximum intensity (singlenorm_int), or the two-pass normalization removing peaks whose height is correlated with scan and using the most intense peaks (doublenorm).
**B**: The difference of the normalization factors obtained from either doublenorm or singlenorm_int compared to singlenorm.
:::

::: {custom-style="MDPI_2.2_heading2"}
### 2.7. Mitigation of High Peak Density Artifacts
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.8. Changes in Relative Standard Deviation (RSD)
:::

@@

::: {custom-style="MDPI_3.1_text"}
Each step in the peak characterization either changes the overall number of peaks coming from each scan (sliding windows and breaking initial regions) or the overall intensity of the points within a scan.
Therefore, one way to quantify any potential *improvements* in the characterized peaks is to look at the relative standard deviation (RSD) for the characterized scan level peak intensities (calculated as the standard deviation of peak heights across scans divided by the mean peak height) and compare them as each processing step is introduced.
`r figure_count$label_text("rsd_method")` illustrates the peak height RSD distributions for four different samples.
Up to two modes are reported for each distribution, where a mode location is only reported if it is ≥ 0.2X the most intense mode.
For samples 1ecf and 2ecf, there is a general shift in the RSD to the left, going from the bottom processing methods (msnbase_only) to the top processing method (filtersd), representing a visually clear improvement.
For samples 49lipid and 97lipid, the improvements are visually more subtle, having a slight shift to the left as well as a narrowing and smoothing of the RSD distribution.
The narrowing of the distribution is detected in the change of the standard deviations (SD) of the RSDs.
Part of this visual subtlety is likely due to the bi-modality of these two distributions.
This is not surprising, since these two samples are non-polar extractions from tissue and are biochemically more complex.
`r table_count$label_text("rsd_method")` provides more quantitative metrics.
At two decimal places, the filtersd, doublenorm, and singlenorm processing methods give superior and nearly identical results for three of the four samples, especially in terms of mean and median RSD.
However, for sample 1ecf, the max RSD is much higher for singlenorm, highlighting its instability.
:::

@@

::: {custom-style="MDPI_4.1_table_caption"}
`r table_count$label_text("rsd_method")`.
RSD means, standard deviations (sd), medians, modes, and maximum observed values for each sample with different overall processing.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.9. Difference to Relative Natural Abundance
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.10. Method Specific Peaks
:::

@@

`r figure_count$label_text("assigned_mz_diff")` shows the distribution of differences between the observed and expected m/z of assigned peaks in the 1ecf and 97lipid spectra.
For the 1ecf-specific histograms, it is clear that these differences have a narrower unimodal distribution from the scan-centric peak characterization, especially in comparison to MSnbase.
Also, the MSnbase distribution has far fewer peaks that match a scan-level assigned peak.
Given the large number of MSnbase-characterized peaks present in the spectrum, many peaks may be outside the matching tolerance of 2ppm. 
This strongly implies that the peak center error is far higher in the MSnbase-characterized peaks than what the histogram directly shows.
For the 97lipid-specific histograms, again the difference distribution for the scan-centric peak characterization is narrower, but the improvement is not as pronounced, likely due to the distribution being bi-modal.
Also, far fewer Xcalibur and MSnbase characterized peaks matched assigned scan-centric peaks.
Again, this strongly implies that their peak centers have far higher error.
When we matched assigned peaks across the NSCLC samples for examination of changes in p-values (see **Changes in P-Values On a Large Dataset**), the standard deviation of the peak locations in frequency space was 0.5 (results not shown).
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.11. Changes in P-Values On a Large Dataset
:::

@@

compare_sina = lung_compare %>%
  ggplot(aes(x = compare_id, y = p_diff)) +
  geom_hline(yintercept = 0, color = "red") +
  geom_sina(alpha = 0.5) +
  geom_point(data = long_measure, aes(x = compare_id, y = value), color = "green") +
  geom_text(data = long_pvalue, aes(x = compare_id, y = 2, label = format(value, digits = 2))) +
  labs(x = "", y = "Log-P-Value Difference")

@@

::: {custom-style="MDPI_2.2_heading2"}
### 2.12. Quality Control and Quality Analysis
:::

@@

The conversion of m/z to frequency also provides opportunities to evaluate each scan and whether it should be kept for further processing.
Checks that have helped us in the development of the scan-centric peak characterization have included: (a) verifying that the ordering of data points remains identical in m/z and frequency space after conversion to frequency; and (b) examining the R^2^ fit of the predicted frequency points to the original frequency points across scans for outliers.
A third quality control step is to examine the coefficients of the square-root term for each scan (see term **y** in Equation `r equation_count$label_text("mzfrequency")`) and look for any outliers, and remove them before continuing the sample processing.
Across the `r length(coefficients_qcqa$n_coef_out)` NSCLC raw files that completed scan-centric processing, `r sum(coefficients_qcqa$n_coef_out > 0)` had at least one scan removed based on the square-root coefficient.
`r figure_count$label_text("coefficients_qcqa")`A shows a histogram of the number of scans removed based on being outliers of the overall distribution.
`r figure_count$label_text("coefficients_qcqa")`B shows what outlier scan coefficients look like in a single sample.
:::

@@

::: {custom-style="MDPI_3.1_text"}
Finally, in the scan-scan normalization step, we require that there be at least 25 peaks in each of the scans that can be used to calculate normalization factors between the scans and the reference scan.
If there are no scans with at least 25 peaks, then the processing of that sample will error and stop.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.1. Samples and Overall Processing
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.2. Matching Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.3. Conversion of m/z to Frequency
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.4. Frequency Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.5. Interval Range Based Data
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.6. Peak Containing Intervals
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.7. Peak Detection and Centroided Values
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.8. Scan to Scan Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.9. Full Scan-Centric Characterization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.10. Correction of Height and Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.11. Marking High Frequency Standard Deviation Peaks
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.12. Calculation of Relative Standard Deviation
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.13. Scan-Centric Peak Assignment
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.14. Consistently Assigned Lipid Spectral Feature (Corresponded Peak) Generation and Peak Intensity Normalization
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.15. Peak - Peak NAP Height Ratios
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.16. Differential Analysis of Large Dataset
:::

@@

Of the starting 181 samples, nine did not finish during scan-centric characterization for various reasons.
In addition, some of the samples were acquired multiple times, creating duplicate samples.
Not knowing which sample run was most appropriate to use, we removed all of the duplicated samples.
Using information-content-informed Kendall-tau correlation (ICI-Kt) [@flightInformationContentInformedKendalltauCorrelation2022], we compared the median correlations of each sample to all others in the same disease class for outliers, and removed `r n_out_vector["cancer"]` cancer and `r n_out_vector["non-cancer"]` non-cancer samples.
The median ICI-Kt correlations are shown in `r supp_figure_count$label_text("icikt_outlier")`.

@@

::: {custom-style="MDPI_2.2_heading2"}
### 4.17. Software Used
:::
